Convex Surrogates via Polyhedral Losses

### 2019-02-02 cvx-fin.tex
Fixed typo and formatting

  For the normals $v_i$ and $v_{i+2}$ such that $\theta_{i,i+2} \leq 120^o$, there is no way for the H-representation $(V, T_{i+1})$ to be tight. \jessie{.....}

  Therefore, there is no $V$ yielding a $2$-construction for abstain and $\alpha > 1/2$.

  Like the triangle observed in the previous proof, we observe that, on the regular hexagon, $T_1$ is a trapezoid with some constraints that are not tight.
\end{proof}

>>>>

  For the normals $v_i$ and $v_{i+2}$ such that $\theta_{i,i+2} \leq 120^o$, there is no way for the H-representation $(V, T_{i+1})$ to be tight. \jessie{justify...}

  Therefore, there is no $V$ yielding a $2$-construction for abstain on $6$ outcomes with $\alpha > 1/2$.
  (Like the triangle observed in the previous proof, we observe that, on the regular hexagon, $T_1$ is a trapezoid with some constraints that are not tight.)
\end{proof}
